{{< var titll >}}

### 2024-09-23 index.qmd
abc

---
title: "{{< var titll >}}"
output: github_document
execute: 
  cache: false
webr:
  show-startup-message: true      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom','cowplot'] 
  cell-options:
    autorun: true
filters:
  - panelize
  - pyodide
  - webr
---

>>>>

---
title: "{{< var titll >}}"
output: github_document
execute: 
  cache: false
#webr:
#  show-startup-message: true      # Display status of webR initialization
#  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
#  packages: ['ggplot2','dplyr','data.table','readr','plotly','combinat','htmltools','broom','cowplot'] 
#  cell-options:
#    autorun: true
filters:
  - panelize
  - pyodide
---
